\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2020-06-03 sections/results.tex
Changes from overleaf

  % TODO: Talk about the datasets: real, mock and synthetic (with references)
  In addition to the algorithmic pipeline itself, our analysis involves two types of data: The first type consists of sets of 16S sequencing data for real communities (see Methods). The second are datasets artificially created for the specific goal of helping evaluate computational analysis tools. In particular, in order to objectively compare, to the extent possible, how well each step in \ac{micone} best captures the underlying data, we use both mock data from mockrobiota~\cite{Bokulich2016} as well as, synthetically generated reads from an Illumina read simulator called ART~\cite{Huang2012}.
  The mock datasets selected were labelled mock4, mock12 and mock16 in the mockrobiota database and consist of sequenced 16S data from mock communities of various bacteria.
  These datasets were selected since they contained the expected compositions along with the reference sequences for the organisms in the mock community.
  The synthetic reads were simulated using the three different taxonomy distribution profiles obtained from soil, water and healthy stool microbiome datasets \hl{[ref]}.
  Reference sequences were generated using \ac{ncbi} and the decard tool \cite{Golob2017} for these taxonomy profiles.
  Detailed information on the mock communities and the settings used to generate the synthetic data are provided in the Methods section.

>>>>

  % TODO: Talk about the datasets: real, mock and synthetic (with references)
  In addition to the algorithmic pipeline itself, our analysis involves two types of data: The first type consists of sets of 16S sequencing data for real communities (see Methods). The second are datasets artificially created for the specific goal of helping evaluate computational analysis tools. In particular, in order to objectively compare, to the extent possible, how well each step in \ac{micone} best captures the underlying data, we use both mock data from mockrobiota~\cite{Bokulich2016} as well as, synthetically generated reads from an Illumina read simulator called ART~\cite{Huang2012}.
  The mock datasets selected were labelled mock4, mock12 and mock16 in the mockrobiota database and consist of sequenced 16S data from mock communities of various bacteria.
  These datasets were selected since they contained the expected compositions along with the reference sequences for the organisms in the mock community.
  The synthetic reads were simulated using the three different taxonomy distribution profiles obtained from soil, water and healthy stool microbiome datasets \hl{[refs]}.
  Reference sequences were generated using \ac{ncbi} and the Decard tool \cite{Golob2017} for these taxonomy profiles.
  Detailed information on the mock communities and the settings used to generate the synthetic data are provided in the Methods section.
